Polymethylation Scores for Prenatal Maternal Smoke Exposure Persist Until Age

### 2021-09-08 Reports/Poster/IGES_poster_vertical.Rmd
drafted poster for iges

---
title: Polymethylation Scores for Prenatal Maternal Smoke Exposure Persist Until Age 15 and Are Detected in Saliva
author:
  - name: Freida Blostein
    affil: 1
    twitter: blostein
    email: blostein@umich.edu
    orcid: 0000-0002-1099-3857
    main: true
  - name: Jonah Fisher
    affil: 2
  - name: John Dou
    affil: 1
  - name: Lisa Schenper
    affil: 3
  - name: Daniel A. Notterman
    affil: 3
  - name: Colter Mitchell
    affil: 2
  - name: Kelly M. Bakulski
    affil: 1
affiliation:
  - num: 1
    address: Department of Epidemiology, University of Michigan School of Public Health, Ann Arbor, Michigan, USA
  - num: 2
    address: Institute for Social Research, University of Michigan, Ann Arbor, Michigan, USA
  - num: 3
    address: Department of Molecular Biology, Princeton University, Princeton, New Jersey, USA
main_findings:
  - "Make **better posters** with RMarkdown + **posterdown**."
  - '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png){.main_pic}'
logoleft_name: '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png){.main-img-left}'
logoright_name: '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png){.main-img-right}'
output: 
  posterdown::posterdown_betterland:
    self_contained: false
    pandoc_args: --mathjax
    highlight: haddock
    number_sections: false
link-citations: true
bibliography: packages.bib
---

```{r, include=FALSE}
knitr::opts_chunk$set(results = 'asis',
                      echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

```{r myplot, include=FALSE}
svg('myplot.svg')
plot(iris$Sepal.Length, iris$Sepal.Width)
dev.off()
```

@@

This is the `posterdown_betterland` template for the {posterdown} package! I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown]. If you're not an R user don't sweat as you do **NOT** need to use it at all! Feel free to use only the Markdown functionality of this package :)

@@

## Objectives

@@

<br>

@@

```{r myprettycode, echo=FALSE,collapse=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=3.5, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

@@

```{r, iristable}
knitr::kable(
  iris[1:8,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

>>>>

---
main_topsize: 0.1 #percent coverage of the poster
main_bottomsize: 0.05
#ESSENTIALS
title: Polymethylation Scores for Prenatal Maternal Smoke Exposure Persist Until Age
  15 and Are Detected in Saliva
title_textsize: 100
author:
- name: Freida Blostein
  affil: 1
  twitter: blostein
  email: blostein@umich.edu
  orcid: 0000-0002-1099-3857
  main: yes
- name: Jonah Fisher
  affil: 2
- name: John Dou
  affil: 1
- name: Lisa Schenper
  affil: 3
- name: Daniel A. Notterman
  affil: 3
- name: Colter Mitchell
  affil: 2
- name: Kelly M. Bakulski
  affil: 1
affiliation:
- num: 1
  address: Department of Epidemiology, University of Michigan School of Public Health,
    Ann Arbor, Michigan, USA
- num: 2
  address: Institute for Social Research, University of Michigan, Ann Arbor, Michigan,
    USA
- num: 3
  address: Department of Molecular Biology, Princeton University, Princeton, New Jersey,
    USA
main_findings:
  - "**Polymethylation scores** for prenatal maternal smoke exposure **persist over time** and are **robust across ancestries**"
logoleft_name: 'Images/Epid_informal_horiz_white.png'
logoright_name: 'Images/Fragile_Families_Logo.png'
logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
primary_colour: "#0048A4"
secondary_colour: "#5885AF"
accent_colour: "#E35A01"
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---

<style>
#main-img-left {
 width: 20%
}
#main-img-center {
 width: 2%
}
#main-img-right {
width=20%
}
</style>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

@@

This is the `posterdown_betterport` template for the {posterdown} package! I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown]. If you're not an R user don't sweat as you do **NOT** need to use it at all! Feel free to use only the Markdown functionality of this package :)

@@

## Gaps

@@

@@

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

@@

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```
